The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-16 paper.tex
update

 Followed by the forward shock is a turbulent and hot plasma.\
 The full extent of the hot plasma is approximately agree with the observation \citep{Su2010}.
 Moreover, the temperature of the plasma is high as 2 keV, comparable to that of the \textit{Fermi} bubbles\
 by observing X-ray absorption lines through the hot\
 gaseous halo along many different sight lines in the sky \citep{Miller_2013}.\

>>>>

 Followed by the forward shock is a turbulent and hot plasma.\
 The full extent of the hot plasma is approximately agree with the observation \citep{Su2010}.
 Also, the temperature of the plasma is high as 2 keV, comparable to that of the \textit{Fermi} bubbles\
 by observing X-ray absorption lines through the hot\
 gaseous halo along many different sight lines in the sky \citep{Miller_2013}.\

 % pressure balance, contact discontinuity
